---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# gridutils

<!-- badges: start -->
<!-- badges: end -->

This package is just my personal practice to play with grid.

## Installation

``` r
# install.packages("devtools")
devtools::install_github("yutannihilation/gridutils")
```

## Usages

### `gu_you_are_here()`

Highlight the current viewport. Unlike `grid::showViewport()`, the highlight is removed after a while.

```{r eval=FALSE}
gu_you_are_here()
```

### `gu_print_vp()`

```{r}
library(gridutils)

library(ggplot2)
library(grid)

p <- ggplot(mtcars, aes(wt, mpg))
p + geom_point() + facet_wrap(~ cyl)
gu_print_vp()
```

## Resources about grid

* [R Graphics, Third Edition](https://www.crcpress.com/R-Graphics-Third-Edition/Murrell/p/book/9781498789059) by Paul Murrel
* [Getting to Know grid Graphics](https://www.stat.auckland.ac.nz/~paul/useR2015-grid/grid-slides.html) by Paul Murrel
* [Mastering Software Development in R](https://bookdown.org/rdpeng/RProgDA/the-grid-package.html) by Roger D. Peng, Sean Kross, and Brooke Anderson

## The internals

### Grob

